\papertitle

### 2012-10-12 manuscript.tex
moved text around

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{System Model}

@@

@@

@@

The task we chose to test our cooperative visual servoing system with is a 
simple target seeking one: the H$^2$Bird must fly through a specified obstacle,
in this case, a wooden frame meant to simulate a window. As the H$^2$Bird does
cannot detect the target on its own, it depends on remote guidance from the
base station. Ground truth data was collected via a motion capture system in
the test room. A sketch of the experimental setup is shown below in Fig.~\ref{fig:experiment_cartoon}.

% TODO clarify or roll into paragraph
Trials were run as follows:
\begin{enumerate}
\item The window is identified by a user. 
\item The H$^2$Bird is released in view of the camera by hand.
\item The H$^2$Bird attempts to fly to the window with remote guidance from
the base station.
\end{enumerate}

% TODO Fill in test # per battery
In total, [50+] good trials were run over a variety of starting positions. 
Variations in the H$^2$Bird hand launch caused the system to respond very 
differently for similar initial conditions. In addition, the H$^2$Bird 
battery was changed approximately every [10] tests, adding more variation to
the H$^2$Bird performance by affecting the motor power output. The effects of 
these noisy factors is considered in Section ~\ref{sec:performance}.

@@

We determined the turning speed and turning radius of the H$^2$Bird
experimentally using the response of the system to the step input of a
clockwise 90 degree turn. We depict the results of this experiment in
Figure~\ref{fig:step_response}.

We gathered the data for the experiment by integrating the output of
H$^2$Bird's on-board gyroscope data. We then used
MATLAB\footnote{\url{http://www.mathworks.com/products/matlab/}} to fit a
simple low-order model (Eq.~\ref{eq:transfer_func}) of the turning
behavior to the step response with the physical heading as the state and the
heading set point as the input. This model serves as a simplification of both
the turning dynamics of the ornithopter and the on-board PID-based attitude
controller. We use this model in Section~\ref{sec:visual_servoing} to
determine the backwards reachable region for navigating through narrow
passages.
\begin{equation}
\label{eq:transfer_func}
H(s) = \frac{0.95}{1+0.62s}
\end{equation}
%TODO H(s) in a labeled equation
%TODO footnote for MATLAB

The step response rise time is approximately 1.4 seconds. The H$^2$Bird
flies at an average forward velocity of 1.2 m/s, so the estimated minimum
turning radius of the robot is 1.07 meters. In experiments, we choose a flight
speed lower than the maximum speed of the ornithopter, to facilitate more
robust tracking.
%TODO equation(s) for how you arrive at the minimum turning radius
%TODO footnote for MATLAB

@@

@@

The geometrically infeasible region is computed using the minimum
turning radius and the geometry of the camera's field-of-view. Both the 
regions in red and blue indicate the infeasible region determined in simulation. 
We ran a simulation on a motion model similar to Dubin's car in ~\cite{lavalle:planning}, with the
angular heading as the input rather than the angular velocity. We used the
turning model, described in Section~\ref{sec:flight_control}, as the input to
the motion model, with a PID controller steering the entire system to the
center of the passage as the input to the tuning model. The infeasible region
calculated in simulation is a superset of the geometrically infeasible region.
The simulation is more realistic as the rotational damping during the turn and
the on-board PID controller cause the real system to react to inputs at a
non-constant angular velocity.

To verify the feasible region experimentally, we conducted trials at initial
distances in approximately 0.4 meter increments from a window along the
edges of the camera image frame. We began each trial with an initial heading
perpendicular to the window plane. The results of the experiments are shown in
Figures~\ref{fig:flight_paths} and~\ref{fig:flight_paths_feasible}.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{System Model}
\label{sec:system_model}

@@

We gathered the data for the experiment by integrating the output of
H$^2$Bird's on-board gyroscope data. We then used
MATLAB\footnote{\url{http://www.mathworks.com/products/matlab/}} to fit a
simple low-order model (Eq.~\ref{eq:transfer_func}) of the turning
behavior to the step response with the physical heading as the state and the
heading set point as the input. This model serves as a simplification of both
the turning dynamics of the ornithopter and the on-board PID-based attitude
controller. We use this model in Section~\ref{sec:visual_servoing} to
determine the backwards reachable region for navigating through narrow
passages.

@@

We determined the turning speed and turning radius of the H$^2$Bird
experimentally using the response of the system to the step input of a
clockwise 90 degree turn. To measure the response of the system, we recorded
the angular position data of the ornithopter calculated from the on-board
gyroscope data.

@@

We tested our cooperative visual servoing system with a simple target seeking
experiment: the H$^2$Bird must fly through a specified obstacle, in this case,
a wooden frame meant to simulate a window. As the H$^2$Bird cannot detect the
target on its own,we used the ground station to provide remote headings for
navigation to the window. Ground truth data was collected via a motion capture
system in the test room. A sketch of the experimental setup is shown in
Fig.~\ref{fig:experiment_cartoon}.

% TODO clarify or roll into paragraph
Each trial included the following steps:
\begin{enumerate}
\item The window is identified by the user. 
\item The H$^2$Bird is released in view of the camera by hand at the desired starting grid point.
\item The H$^2$Bird attempts to fly to the window with remote guidance from
the base station.
\end{enumerate}

In total, 80 trials were run over a variety of starting positions. The goal of our experiments was to verify the model described in~\ref{sec:system_model}, so we conducted 60 of the 80 trials in a grid along the edges of the camera viewplane in 0.05 meter increments from the window to determine the success rate on the edges of the testing space. We conducted 20 additional trials directly in front of the camera to determine the success rate near the center of the testing space. The H$^2$Bird battery was changed approximately every 5 tests, adding more variation to the H$^2$Bird performance by affecting the motor power output.

% Don't think this goes here
Variations in the H$^2$Bird hand launch caused the system to respond 
differently for similar initial conditions. In addition, the H$^2$Bird 
battery was changed approximately every 5 tests, adding more variation to
the H$^2$Bird performance by affecting the motor power output. The effects of 
these noisy factors is considered in Section ~\ref{sec:performance}.
% Might move

@@

We depict the results of this experiment in
Figure~\ref{fig:step_response}.

\begin{equation}
\label{eq:transfer_func}
H(s) = \frac{0.95}{1+0.62s}
\end{equation}
%TODO H(s) in a labeled equation
%TODO footnote for MATLAB

The step response rise time is approximately 1.4 seconds. The H$^2$Bird
flies at an average forward velocity of 1.2 m/s, so the estimated minimum
turning radius of the robot is 1.07 meters. In experiments, we choose a flight
speed lower than the maximum speed of the ornithopter, to facilitate more
robust tracking.

%TODO equation(s) for how you arrive at the minimum turning radius
%TODO footnote for MATLAB

@@

The geometrically infeasible region is computed using the minimum
turning radius and the geometry of the camera's field-of-view. Both the 
regions in red and blue indicate the infeasible region determined in simulation. 
We ran a simulation on a motion model similar to Dubin's car in ~\cite{lavalle:planning}, with the
angular heading as the input rather than the angular velocity. We used the
turning model, described in Section~\ref{sec:flight_control}, as the input to
the motion model, with a PID controller steering the entire system to the
center of the passage as the input to the tuning model.

@@

The infeasible region
calculated in simulation is a superset of the geometrically infeasible region.
The simulation is more realistic as the rotational damping during the turn and
the on-board PID controller cause the real system to react to inputs at a
non-constant angular velocity.

The results of the experiments are shown in
Figures~\ref{fig:flight_paths} and~\ref{fig:flight_paths_feasible}.
